---
title: "HW 4"
author: "Adon Rosen"
date: 'Date: `r Sys.Date()`'
output: pdf_document
---
  
```{r, echo=F, message=F, warning=FALSE}
library(knitr)
opts_knit$set(root.dir='~/Documents/Psych5003/HW4')  #Don't combine this call with any other chunk -especially one that uses file paths.
```


<!-- Set the report-wide options, and point to the external code file. -->
  ```{r set_options, echo=F, warning=FALSE}
# cat("Working directory: ", getwd())
report_render_start_time <- Sys.time()
opts_chunk$set(
  results    = 'show',
  comment    = NA,
  tidy       = FALSE,
  fig.width  = 10,
  fig.height = 6,
  fig.path   = 'figure-png/'
)
# echoChunks <- FALSE
options(width=80) #So the output is 50% wider than the default.
read_chunk("./homeWork4.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```

```{r load-packages, echo=FALSE, results='show', message=FALSE, warning=FALSE}
```
```{r load-data, echo=FALSE, results='show', message=FALSE, warning=FALSE}
```
```{r create-functions, echo=FALSE, results='show', message=FALSE, warning=FALSE}
```

# Question 1
```{r create-marginal-means, echo=FALSE, results='show', warning=FALSE, message=FALSE}
```

# Question 2
```{r plot-data, echo=FALSE, results='show', warning=FALSE, message=FALSE}
```

# Question 6
```{r run-aov, echo=TRUE, results='show', warning=FALSE, message=FALSE}
```

# Question 7
```{r run-simple-effect, echo=TRUE, results='show', warning=FALSE, message=FALSE}
```

# Question 8
Differences in drug dosage effects were tested differentially across the sexes utilizing a two way analysis of variance. Dosage was coded as a five level factor with greater values indicating greater dosage, sex was coded as a two level factor. The resultant interaction was found to be significant (F(4,99)=5.9, p<.001) indicating the sexes respond differentially to level of the drug. It is important to note that under increased dosage both sexes did display greater scores and sex was shown to be a significant main effect too (F_sex=29.94, p<0.001; F_dosage=47.2, P<0.001). Further post-hoc t-tests were used to test where the differences emerged across the discrete dose categorizations. While lower levels of does (levels 1,2) did not display significant differences between the sexes (t_1(18)=.68, p>0.05; t_2(18)=-.76, p>0.05), differences in greater dose levels were observed (t_3(18)=-2.80, p=0.01; t_4(18)=-2.56, p=0.02; t_5(18)=-5.02, p<.001). These results suggest greater scores were observed in the female cohort under greater dosage levels than the male cohorts.