---
title: "HW 3"
author: "Adon Rosen"
date: 'Date: `r Sys.Date()`'
output:
  word_document: pdf
---

--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F, warning=FALSE, echo=F}
# cat("Working directory: ", getwd())
  library(knitr)
  opts_knit$set(root.dir='~/Documents/Psych5003/HW3')  #Don't combine this call with any other chunk -especially one that uses file paths.
```


<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F, warning=FALSE}
# cat("Working directory: ", getwd())
report_render_start_time <- Sys.time()
opts_chunk$set(
  results    = 'show',
  comment    = NA,
  tidy       = FALSE,
  fig.width  = 10,
  fig.height = 6,
  fig.path   = 'figure-png/'
)
# echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
read_chunk("./homeWork3.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```

```{r load-packages, echo=FALSE, results='show', message=FALSE, warning=FALSE}
```
```{r load-data, echo=FALSE, results='show', message=FALSE, warning=FALSE}
```

```{r q-1b, echo=FALSE, results='show', message=FALSE, warning=FALSE}
```

### Question 1b
Here utiliizng a t test to explore differences in means between the two gender groups, we conclude the differences in salary do display significant differences across genders. The resultant models statisc was `r base::print(to.report.stat)` with a p value of `r base::round(base::print(to.report.prob), 5)`. This value reflects the probability of observing this difference in means given there is no difference between the two groups.

### Question 1c
Here utilizing a variance test to explore differences in group variance, we fail to reject the null hypothesis that the genders display equivalent variance. The resultant models statisc was `r base::print(to.report.stat)` with a p value of `r base::round(base::print(to.report.prob), 5)`. 

### Question 1d

