---
title: "HW 3"
author: "Adon Rosen"
date: 'Date: `r Sys.Date()`'
output: pdf_document
---

```{r, echo=F, message=F, warning=FALSE}
# cat("Working directory: ", getwd())
  library(knitr)
  opts_knit$set(root.dir='~/Documents/Psych5003/HW3')  #Don't combine this call with any other chunk -especially one that uses file paths.
```


<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F, warning=FALSE}
# cat("Working directory: ", getwd())
report_render_start_time <- Sys.time()
opts_chunk$set(
  results    = 'show',
  comment    = NA,
  tidy       = FALSE,
  fig.width  = 10,
  fig.height = 6,
  fig.path   = 'figure-png/'
)
# echoChunks <- FALSE
options(width=80) #So the output is 50% wider than the default.
read_chunk("./homeWork3.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```

```{r load-packages, echo=FALSE, results='show', message=FALSE, warning=FALSE}
```
```{r load-data, echo=FALSE, results='show', message=FALSE, warning=FALSE}
```
```{r create-functions, echo=FALSE, results='show', message=FALSE, warning=FALSE}
```

# Question 1
### Question 1a
```{r q-1a, echo=TRUE, results='show', message=FALSE, warning=FALSE}
```

### Question 1b
```{r q-1b, echo=TRUE, results='show', message=FALSE, warning=FALSE}
```
Here utiliizng a t test to explore differences in means between the two gender groups, we conclude the differences in salary do display significant differences across genders. The resultant models statistic was `r base::round(print(to.report.stat),2)` with a p value of `r base::round(base::print(to.report.prob), 5)`. This value reflects the probability of observing this difference in means given there is no difference between the two groups.

### Question 1c
```{r q-1c, echo=FALSE, results='show', message=FALSE, warning=FALSE}
```
Here utilizing a variance test to explore differences in group variance, we fail to reject the null hypothesis that the genders display equivalent variance. The resultant models statisc was `r base::round(print(to.report.stat),2)` with a p value of `r base::round(base::print(to.report.prob), 5)`. 

### Question 1d
Here, utilizing this publicly available data, we tested for differences in means between female and male colleagues. First, assumptions for a parametric t test were checked by measuring for differences in sample variance using an f-test, here we observed a nonsignificant difference in variance between the two populations (F(99,199)=.79, p=.19). With this assumption met, significant differences in means were observed using a t test (t(219)=17, p<.0005). This value suggested that male colleagues have greater mean salaries than their female counter parts.

# Question 2
### Question 2a

#### Report my hypotheses here:
$$H_0 : \mu_1 = \mu_2 = \mu_3$$
$$H_a : \mu_i \neq \mu_j  \text{ For some i and j}\\ $$


```{r q-2a, echo=TRUE, results='show', message=FALSE, warning=FALSE}
```

Here, we will reject the null hypothesis stating that these populations display equivalent means given our F statistic of `r base::round(print(f.stat), 2)` which has a p value of `r base::round(print(f.stat.p.val), 5)`

### Question 2b
```{r q-2b, echo=TRUE, results='show', message=FALSE, warning=FALSE}
```

# Question 3
```{r q-3a, echo=TRUE, results='show', message=FALSE, warning=FALSE}
```